WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/Manuscript_DS.Rmd
R1 C8 What does worcs do?

We provide a conceptual outline of the WORCS procedure below, based on WORCS
Version 0.1.5.
Note that, although the steps are numbered for reference purposes,
we acknowledge that the process of conducting research is not always linear.
For users of the `worcs` `R` package, we highly recommend referring to
[the workflow vignette](https://cjvanlissa.github.io/worcs/articles/setup.html),
which is more detailed and updated with future developments.
For an up-to-date list of sample `worcs` projects, see the [WORCS GitHub page](https://github.com/cjvanlissa/worcs).

>>>>

We provide a conceptual outline of the WORCS procedure below, based on WORCS
Version 0.1.5.
The conceptual workflow recommends actions to take 
in the different phases of a research project, in order to work openly and transparently
in compliance with the TOP-guidelines and best practices for open science.
Note that, although the steps are numbered for reference purposes,
we acknowledge that the process of conducting research is not always linear.
We refer users of the `worcs` implementation in `R` to
[the workflow vignette](https://cjvanlissa.github.io/worcs/articles/setup.html),
which describes in more detail which steps are automated by the `R` package
and which actions must be taken by the user.
The vignette is also updated with future developments of the package.

For an up-to-date list of sample `worcs` projects, see the [WORCS GitHub page](https://github.com/cjvanlissa/worcs).

### 2020-11-03 paper/reviews_ds.Rmd
R1 C8 What does worcs do?

\RC{In the 3 phases listed, it is not clear what worcs does and does not for users.}

\Assignment{All}
\WorkInProgress
\Medium

>>>>

\RC{C8: In the 3 phases listed, it is not clear what worcs does and does not for users.}

Response: It is not entirely clear to us whether the Reviewer is referring to the conceptual workflow ("WORCS"), or to the `R` implementation of WORCS, i.e., `worcs`.

We suspect that the Reviewer means the `worcs` R-package, so to address this comment,
the Revision now states the following:

> For users of the `worcs` `R` package, we highly recommend referring to
[the workflow vignette](https://cjvanlissa.github.io/worcs/articles/setup.html),
which describes in more detail which steps are automated by the `R` package
and which actions must be taken by the user.
The vignette is also updated with future developments of the package.

Just in case we misunderstood, and the Reviewer actually meant the conceptual workflow WORCS, we have also added a few sentences to clarify the purpose of the conceptual workflow:

> We provide a conceptual outline of the WORCS procedure below, based on WORCS
Version 0.1.5.
The conceptual workflow recommends actions to take 
in the different phases of a research project, in order to work openly and transparently
in compliance with the TOP-guidelines and best practices for open science.
Note that, although the steps are numbered for reference purposes,
we acknowledge that the process of conducting research is not always linear.
